Discriminative Sensing Based on Signal Processing

### 2017-10-22 docs/thesis/chapters/2_pca_svm_cfa/pca_svm_cfa.tex
one more step

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) for visual discriminative analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

To the best of our knowledge, we are the first to propose a critical factors analysis based on PCA for visual discriminative analysis and based on RFE combined with SVM for CSF identification from IT governance data.

@@

The Federal Court of Accounts (TCU, in Portuguese) surveys data of IT practices of brazilian public organizations in order to audit IT governance. This resulting dataset is called iGovTI. We propose to use the iGovTI of 2012 for CSF analysis. The iGovTI is composed by 201 questions used for organization ranking according to their responses and their IT governance.

This section presents details of the experimental scenario and describes the dataset model used to evaluate our proposal. Subsection \ref{sec:DataCollection} describes the environment and scenario adopted in order to reproduce flood and probe attacks. Subsection \ref{sec:ModelingData} presents how network traffic can be modeled as signal superposition. Subsection \ref{sec:SynfloodFraggleandPortscan} details the traffic of synflood, fraggle and port scan attacks, and Subsection \ref{sec:DarpaDataset} discusses the use of the DARPA dataset for evaluation of the proposed approach.

\section{Discriminative...}
\label{sec:prop_getv}

In this section we evaluate the PCA for data visualization and identification of critical factors of the evaluated dataset. Futhermore, we propose a

\subsection{Principal Component Analysis}

PCA is a statistical technique commonly used for dimensionality reduction. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance. PCA is a common technique for finding patterns in data of high dimension and for highlighting its discrinative characteristics and strucutres, throught an orthogonal basis transformation into new basis, by diagonalizing the centered covariance matrix of a data set {Xk E RNlk = 1, ... ,f}, defined by C = ((Xi - (Xk))(Xi - (Xk))T). The coordinates in the Eigenvector basis are called principal components. The size of an Eigenvalue >. corresponding to an Eigenvector v of C equals the amount of variance in the direction of v. PCA is usually used for signal denoising, blind source separation, data compression, data visualization, feature extraction and dimensionality reduction, where a reduced number of features is extrated retaining as much information as possible \cite{jolliffe1986principal}.

@@

\subsection{Suport Vector Machines}

@@

\subsection{Recursive Feature Elimination}

@@

 Quadro 7 – Autovalores  Ordem dos autovalores  Autovalores da variância explicada Autovalores acumulados da variância explicada acumulada
Fonte: Dados da Pesquisa

@@

Gráfico 1 – Ranking dos autovalores
Fonte: Dados da pesquisa

@@

Gráfico 2 – Relação entre os  e  
Fonte: Dados da pesquisa

@@

Gráfico 3 – Relação entre os ,  e 
Fonte: Dados da pesquisa

@@

Quadro 8 – Variáveis com alta significância CP1 a CP20
Fonte: Dados da pesquisa

@@

Quadro 9 – Variáveis com alta significância CP 21 a CP 51
Fonte: Dados da pesquisa

@@

Gráfico 4 – Dados brutos da pesquisa
Fonte: Dados da pesquisa

@@

Gráfico 5 – Destaque de corte nas instituições 
Fonte: Dados da pesquisa

@@

\section{Conclusion}

>>>>

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) for visual discriminant analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

This chapter is organized as follows. In Section \ref{sec:relatedworks}, related works are discussed. Section \ref{sec:datamodel} presents the data model and the evaluated datasets. Section \ref{sec:csf_fs} describes the proposed approach for critical success factors analysis. Section \ref{sec:experimentalresults} discusses the experimental validation and presents the results, and Section \ref{sec:conclusion} draws the conclusions.

@@

To the best of our knowledge, we are the first to propose a critical factors analysis based on PCA for visual discriminant analysis and based on RFE combined with SVM for CSF identification from IT governance data.

@@

The brazilian Federal Court of Accounts (TCU, in Portuguese) surveys data regarding IT practices of brazilian public organizations in order to audit IT governance. The dataset with a consolidate view about the answers for this surgey the IT governance index is called iGovTI. The iGovTI is composed by 201 multiple choice questions, used for ranking according to their IT governance, submmited to 349 organizations. The TCU computes the IT governance index and classifies the IT governace of each organization. Additionally, Ramos \emph{et al} \cite{ramos2016information} classifies each question regarding its relevance for IT governance through a qualitative analysis, and identify the CSFs for selected IT managers regarding IT governance.

\section{An approach for Critical Success Factors Analysis}
\label{sec:csf_fs}

In this section we propose an approach for Critical Success Factors Analysis based on visual discriminant analysis and based on feature selection, in orde to identify the CSFs for IT governance according to iGovTI. Initially we conduct an analysis based on PCA to evaluate the relevante of each feature according to their variance, and use the 2 most relevant features for a visualization of the iGovTI ranking. Furthermore, we propose a critical success factors analysis based on SVM for classification and based on RFE for identification of the most relevant factors.

\subsection{Visual Discriminant Analysis based on PCA}

PCA is a statistical technique commonly used for dimensionality reduction. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance.

PCA is also used for finding patterns in data of high dimension and for highlighting its discrinative characteristics and strucutres, throught an orthogonal basis transformation into new basis, by diagonalizing the centered covariance matrix of a data set {Xk E RNlk = 1, ... ,f}, defined by C = ((Xi - (Xk))(Xi - (Xk))T). The coordinates in the Eigenvector basis are called principal components. The size of an Eigenvalue >. corresponding to an Eigenvector v of C equals the amount of variance in the direction of v. PCA is usually used for signal denoising, blind source separation, data compression, data visualization, feature extraction and dimensionality reduction, where a reduced number of features is extrated retaining as much information as possible \cite{jolliffe1986principal}.

@@

\subsection{iGovTI classification}

@@

\subsection{CSF analysis based on SVM-RFE}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=6cm, width=9cm]{figures/pca-svm-rfe_raw_variance_ecdf.eps}
     \caption{Empirical CDF of variance.}
     \label{fig:fig1}
\end{figure}

@@

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=6cm, width=9cm]{figures/pca-svm-rfe_raw_igovti_ranking_pc2.eps}
     \caption{iGovTI ranking from 2 principal components.}
     \label{fig:fig1}
\end{figure}

@@

@@

@@

@@

@@

@@

\section{Conclusion}
\label{sec:conclusion}
